Deciding to Disclose

### 2015-06-02 Background.tex
Reflecting reviewers comments

While game theory addresses rational \emph{strategic} decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.  Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem. An complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}. Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

>>>>

While game theory addresses rational \emph{strategic} decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.  Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem. A complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}. Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

### 2015-06-02 Introduction.tex
Reflecting reviewers comments

Turning more specifically to disclosure of alcohol use during pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}. The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking. The simulation model described in this paper is able to replicate both qualitative trends, i.e. an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.

The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where \acp{RCT} are not viable for ethical, or financial reasons. With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.

@@

While there is no universal theory of human behaviour to sit at the centre of \ac{ABM}ing as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, decision rules represent a pleasingly parsimonious alternative to explicit behavioural rules covering all possible eventualities.

>>>>

Turning more specifically to disclosure of alcohol use by women during their pregnancy, research is relatively sparse, although qualitative trends are reported by \citet{Phillips2007} and \citet{Alvik2006}. The former explored factors impacting disclosure through a small case study, highlighting the need to build up rapport between woman and midwife over several appointments; the latter compared post partum reports of consumption with contemporaneous accounts, finding apparent underreporting during pregnancy which was amplified by increased drinking. The simulation model described in this paper is able to replicate both qualitative trends, i.e. an increase in disclosure over appointments, and more honest behaviour by moderate as compared to heavier drinkers.

The resulting scenario is of substantial independent interest, and shows the potential utility of a simulation approach in arenas where randomized control trials are not viable for ethical, or financial reasons. With this said, the lack of a strong quantitative evidence base against which to validate the behaviour of the model augers for caution in interpreting the results, and a necessary reminder that in this instance the model is primarily a tool for formalisation of the thought process \citep{epstein2008}, rather than a machine for predicting.

@@

While there is no universal theory of human behaviour to sit at the centre of \ac{ABM}ing as a method, a key motivation for decision rules is their claim to provide an account of decision making that is behaviourally and cognitively plausible. Their mooted capability in this regard is to some extent supported by work from neuroeconomics, which aims to empirically test theories of decision making \citep{Rustichini2009}. Many key aspects common to decision rules, for example the idea that a common currency is used by the brain to compare outcomes \citep{Padoa-Schioppa2006,Padoa-Schioppa2008}, are supported by neurological findings. In addition, a single decision rule represents a pleasingly parsimonious alternative to numerous case specific production rules.

### 2015-06-02 Model.tex
Footnote, formula typo
Reflecting reviewers comments

Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period. Outside of caseloading\footnote{Under a caseloading system, women are allocated an individual, or small group of midwives who deal with their care throughout pregnancy, and birth.} teams, a woman does not generally have a named midwife, and may see a different practitioner at each appointment. In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

@@

In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals. We also make the simplifying assumption that a woman may have one of only three drinking patterns - light, moderate, or heavy. Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

@@

%Might belong in a more methody bit? Read some stuff to check..
To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives. Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
Additionally define two utility functions - 
\begin{equation}
u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}},
\end{equation} 
\begin{equation}
u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife. Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.

@@

>>>>

Typically in the UK, a women will have 12 appointments with a midwife during the antenatal period, and in the majority of cases will encounter several different midwives \citep{Redshaw2014} in the course of their care. In the UK, and unlike most healthcare scenarios, maternity notes are held by the patient, so midwives do not have extensive information prior to an appointment unless they have encountered the woman previously. Maternity notes are not generally linked to extra-departmental records, meaning that a history of alcohol related admissions to another service may remain unknown unless revealed by the woman.

@@

In order to translate the scenario sketched above into a more abstract, tractable form, we cast it as a signalling game, and assume that women's disclosures (or not), are signals. We also make the simplifying assumption that a woman may have one of only three drinking patterns - light\footnote{Or abstinent, the extent of alcohol consumption being such that it would generally be felt to pose essentially no risk.}, moderate, or heavy. Correspondingly, they are limited in what signals they may send when claiming to be one of these three types.

@@

@@

%Might belong in a more methody bit? Read some stuff to check..
To formally define the game, let \(N = \{m, w\}\) be the set of players each with a private type \(\theta_{i} \in \Theta\), and a set of types \(\Theta=\{l, m, h\}\), with pure strategies \(A_{m}=\{r,n\}, A_{w}=\{l, m, h\}\). Here, \(\{l, m, h\}\) correspond to light, moderate, and heavy alcohol consumption for women, and non-judgemental, moderately judgemental, and harshly judgemental for midwives. Midwives' pure strategies \(\{r,n\}\) are to refer, or do nothing, and those for women are to signal that they have one of the possible drinking patterns.
Additionally define two utility functions - 
\begin{equation}
u_{w}(s_{w}, s_{m}, \theta_{w}, \theta_{m})=X_{s, s_{w}, \theta_{m}} + X_{h, \theta_{w}, s_{m}}
\end{equation} 
\begin{equation}
u_{m}(s_{w}, s_{m}, \theta_{w})=X_{h, \theta_{w}, s_{m}} + X_{c, \theta_{w}, s_{m}},
\end{equation} with $X_{c}$, $X_{h}$, and $X_{s}$ being the payoff matrices as in table \ref{tab:Payoff-matrix}, $s_{w}$ and $s_{m}$ denoting a specific signal by a woman, and referral response by a midwife. Lastly let \(p_{w}(l, m, h)\), \(p_{m}(l, m, h)\) be distributions over types of women, and midwives respectively.
